Testing Gravity Using Type Ia Supernovae Discovered by Next Generation Wide Field Imaging Surveys

### 2019-02-01 doc/article.tex
fix stupid typo

\begin{document}
%\raggedright
\begin{raggedright}
\huge
Astro2020 Science White Paper \linebreak
proj
Testing Gravity Using Type Ia Supernovae Discovered by Next-Generation Wide-Field Imaging Surveys \linebreak
\normalsize

>>>>

\begin{document}
%\raggedright
\begin{raggedright}
\huge
Astro2020 Science White Paper \linebreak
Testing Gravity Using Type Ia Supernovae Discovered by Next-Generation Wide-Field Imaging Surveys \linebreak
\normalsize
